### 2018-11-15 Sections/quantum_algorithms.tex
explaining the graph for shallow circuits

If we lay out the circuit in 2D (hence the 2D HLF problem), it only requires classically-controlled Clifford gates\index{Clifford gates} between nearest neighbour qubits on a 2D grid. An example is shown in Fig.~\ref{fig:2DHLFgrid}.
\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.4\textwidth]{shallow_circuits_2D}
\caption{\comment{To do. What do symbols all mean?}\label{fig:2DHLFgrid} Implementation of the HLF problem on a 2D grid.}
\end{figure}

>>>>

If we lay out the circuit in 2D (hence the 2D HLF problem), it only requires classically-controlled Clifford gates\index{Clifford gates} between nearest neighbour qubits on a 2D grid. An example is shown in Fig.~\ref{fig:2DHLFgrid}. An instance of the HLF problem can be described by a graph $G(A)$ with $n$ vertices such that the off-diagonal part of A is the adjacency matrix of $G(A)$. Here $A_{i,j}=0$ unless $i,j$ are nearest neighbour vertices of the grid or $i = j$. We place qubits at each vertex and every edge corresponds to an input bit. The HLF problem is solved by applying nearest-neighbour $C_Z$ gates and $S_i$ phase gates at the correct site.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.4\textwidth]{shallow_circuits_2D}
\caption{\label{fig:2DHLFgrid} Implementation of the HLF problem on a 2D grid.}
\end{figure}
